A Survey on Ordered Binary Decision Diagrams

### 2015-09-13 paper.tex
Add unique-table notion to hash table section
Finish ITE operator

This would result in an algorithm having a worst case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} ($ITE$)
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

@@

Moreover, hash tables are useful to generate a reduced graph directly from some
operations by maintaing a hash table associating triples
($var(n)$, $lo(n)$, $hi(n)$) with a single nonterminal node $n$. This is done for
each nonterminal node $n$ generated while executing the
operation~\cite{BRYANT92}.

@@

Accoring to Brace et al.~\cite{BRACE90}, the $ITE$ operator forms the core of an
efficient OBDD package implementation. \tbr

>>>>

This would result in an algorithm having a worst-case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} ($ITE$)
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

@@

Moreover, hash tables are useful to generate a reduced graph directly from some
operations by maintaing a hash table associating triples
($var(n)$, $lo(n)$, $hi(n)$) with a single nonterminal node $n$. This is done for
each nonterminal node $n$ generated while executing the
operation~\cite{BRYANT92}. This is also referred to as
\textit{unique-table}~\cite{BRACE90} imposes the canonical form of an OBDD. If a
new node is generated, a corresponding entry is created in the unique-table.

@@

Accoring to Brace et al.~\cite{BRACE90}, the $ITE$ operator forms the core of an
efficient OBDD package implementation. Hence, they used a hash-based cache, called
\textit{caching computed-table}, to implement it, exploiting a high locality of
reference and consuming less memory.

Compared to using a normal hash table, this results in more recursive calls to 
$ITE$ (because of cache misses) but less time spent in garbage collection
(described in Section~\ref{subsec:garbage-collection}) and look-ups (because no
collision chains need to be searched).

Nevertheless, it is worth noting that the worst-case time complexity increases
to be exponential if all keys are hashed to the same value, compared to a
polynomial time complexity for normal hash tables~\cite{BRACE90}.

Furthermore, Brace et al.~\cite{BRACE90} advise to use \textit{standard triples},
i.e. to define an $ITE(f_1, f_2, f_3)$-based equivalence relation on sets of
three functions $f_1$, $f_2$ and $f_3$. This takes advantage of the fact that
different parameters may yield the same result when $ITE$ is called. Hence, before
the computed-table is accessed when executing $ITE$, the arguments are replaced
by the standard arguments. Using this approach some recomputations can be avoided
and, obviously, less space is consumed by the computed-table~\cite{BRACE90}.

Brace et al.~\cite[p. 42]{BRACE90} provides the pseudocode of the $ITE$ algorithm
as well as a modification, called $ite\_constant$, which can be used to implement
logical implication tests more efficiently by avoiding the construction of
intermediate nodes. \tbr
